Supplementary Analyses

### 2025-09-08 procesamiento/04-prod_prep-supplementary-material.Rmd
update for RR

```{r tableS1, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

@@

ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "gini_disp" = "Income inequality (Gini index)",
              loggdppercapita = "GDP/capita",
              wstate2="Size of the welfare state",
              cpi = "Corruption Index",
              v2x_polyarchy = "Democracy (polyarchy index)",
              mig_share = "Migration (pop %)",
              union_den = "Union density",
              unemployment_rate = "Unemployment rate",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity*Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity*Working Class",
              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity*Intermediate Class*Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity*Working Class*Income Inequality")

htmlreg(models_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       file = here::here("output/tables/tableS02.html"),
       caption = paste("Table S2: Multilevel models for country-level factors,
                       income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars. The depedent variable and country-level variables are in standardized (z-score)",
       caption.above = T,leading.zero = T,single.row = F,threeparttable = T,
       custom.coef.map = ccoef,
      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
      # custom.gof.rows = list("Controls"=rep("Yes",4)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual")
      )
```

@@

# Double cross-level interaction Gini and Welfare State Size (Index)------------
int_xlvl_gini_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         loggdppercapita+
         homclass3_V_gc*dclass3res_V*gini_disp + 
         homclass3_V_gc*dclass3res_V*wstate2 + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

@@

ccoef <- list(homclass3_V_gc="Class-based network homogeneity (CWC)",
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Homogeneity × Intermediate Class",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Homogeneity × Working Class",

              "homclass3_V_gc:gini_disp"= "Homogeneity × Income Inequality",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Homogeneity × Intermediate Class × Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Homogeneity × Working Class × Income Inequality",

              "homclass3_V_gc:ilo_taxrev"= "Homogeneity × (Tax revenue)",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_taxrev" = "Homogeneity × Intermediate Class × (Tax revenue)",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_taxrev" = "Homogeneity × Working Class × (Tax revenue) ",

              "homclass3_V_gc:ilo_govspe"= "Homogeneity × Welfare State (Gov. Spending)",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_govspe" = "Homogeneity × Intermediate Class × (Gov. Spending)",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_govspe" = "Homogeneity × Working Class × (Gov. Spending)",

              "homclass3_V_gc:abs_red"= "Homogeneity × Welfare State (Redistribution)",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):abs_red" = "Homogeneity × Intermediate Class × (Redistribution)",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):abs_red" = "Homogeneity × Working Class × (Redistribution)",

              "homclass3_V_gc:wstate2"= "Homogeneity × Welfare State",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):wstate2" = "Homogeneity × Intermediate Class × Welfare State",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):wstate2" = "Homogeneity × Working Class × Welfare State",

              "homclass3_V_gc:loggdppercapita"= "Homogeneity × GDP",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):loggdppercapita" = "Homogeneity × Intermediate Class × GDP",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):loggdppercapita" = "Homogeneity × Working Class × GDP"              
              )

htmlreg(models_interactions,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       file = here::here("output/tables/tableS03.html"),
       caption = paste("Table S3: Robustness analysis of the multilevel models for income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
       custom.coef.map = ccoef,
      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
      # custom.gof.rows = list("Controls"=rep("Yes",4)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual")
      )
```

@@

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + homclass3_V_res + (1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total +female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass6res)
digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res)
digclas1_VW_8 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res*gini_disp)

digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
                    digclas1_VW_3,
                    # digclas1_VW_4,
                    #digclas1_VW_5,
                    # digclas1_VW_6,
                    digclas1_VW_7)

ccoef <- list(homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",
              "dclass6resLower Service class"="Lower Service",
              "dclass6resRoutine nonmanual class" = "Routine nonmanual",                 
              "dclass6resSelf-employed" = "Self-employed",                           
              "dclass6resSkilled working class" = "Skilled working",
              "dclass6resUnskilled working class" = "Unskilled working",
              "homclass3_V_res:dclass6resLower Service class" = "Homogeneity × Lower Service",
              "homclass3_V_res:dclass6resRoutine nonmanual class" = "Homogeneity × Routine nonmanual",
              "homclass3_V_res:dclass6resSelf-employed"= "Homogeneity × Self-employed",
              "homclass3_V_res:dclass6resSkilled working class" = "Homogeneity × Skilled working class",
              "homclass3_V_res:dclass6resUnskilled working class" = "Homogeneity × Skilled working class" 
              )

@@

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table S4: Multilevel models for network homogeneity and redistributive preferences (6-class version)"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       groups =
         list("Social Class (Ref.= Upper Service)" = 3:7,
              "Homogeneity × Social Class"=8:11),
      custom.gof.rows = list("Controls"=c("No",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/tableS04.html")
      )
```

@@

ccoef <- list(homclass3_V_gc="Class-based network homogeneity",
              know_total="Network size",
              "dclass6resLower Service class"="Lower Service",
              "dclass6resRoutine nonmanual class" = "Routine nonmanual",                 
              "dclass6resSelf-employed" = "Self-employed",                           
              "dclass6resSkilled working class" = "Skilled working",
              "dclass6resUnskilled working class" = "Unskilled working",
              "homclass3_V_gc:dclass6resLower Service class" = "Homogeneity × Lower Service",
              "homclass3_V_gc:dclass6resRoutine nonmanual class" = "Homogeneity × Routine nonmanual",
              "homclass3_V_gc:dclass6resSelf-employed"= "Homogeneity × Self-employed",
              "homclass3_V_gc:dclass6resSkilled working class" = "Homogeneity × Skilled working class",
              "homclass3_V_gc:dclass6resUnskilled working class" = "Homogeneity × Skilled working class",

@@

              # 3-way interactions: × Gini
              "homclass3_V_gc:dclass6resLower Service class:gini_disp"         = "Homogeneity × Lower Service × Gini",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:gini_disp"     = "Homogeneity × Routine Nonmanual × Gini",
              "homclass3_V_gc:dclass6resSelf-employed:gini_disp"               = "Homogeneity × Self-employed × Gini",
              "homclass3_V_gc:dclass6resSkilled working class:gini_disp"       = "Homogeneity × Skilled Working Class × Gini",
              "homclass3_V_gc:dclass6resUnskilled working class:gini_disp"     = "Homogeneity × Unskilled Working Class × Gini",

              # 3-way interactions: × Tax Revenue
              "homclass3_V_gc:dclass6resLower Service class:ilo_taxrev"         = "Homogeneity × Lower Service × Tax Revenue",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:ilo_taxrev"     = "Homogeneity × Routine Nonmanual × Tax Revenue",
              "homclass3_V_gc:dclass6resSelf-employed:ilo_taxrev"               = "Homogeneity × Self-employed × Tax Revenue",
              "homclass3_V_gc:dclass6resSkilled working class:ilo_taxrev"       = "Homogeneity × Skilled Working Class × Tax Revenue",
              "homclass3_V_gc:dclass6resUnskilled working class:ilo_taxrev"     = "Homogeneity × Unskilled Working Class × Tax Revenue",

              # 3-way interactions: × Government Spending
              "homclass3_V_gc:dclass6resLower Service class:ilo_govspe"         = "Homogeneity × Lower Service × Gov. Spending",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:ilo_govspe"     = "Homogeneity × Routine Nonmanual × Gov. Spending",
              "homclass3_V_gc:dclass6resSelf-employed:ilo_govspe"               = "Homogeneity × Self-employed × Gov. Spending",
              "homclass3_V_gc:dclass6resSkilled working class:ilo_govspe"       = "Homogeneity × Skilled Working Class × Gov. Spending",
              "homclass3_V_gc:dclass6resUnskilled working class:ilo_govspe"     = "Homogeneity × Unskilled Working Class × Gov. Spending",

              # 3-way interactions: × Redistribution
              "homclass3_V_gc:dclass6resLower Service class:abs_red"         = "Homogeneity × Lower Service × Redistribution",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:abs_red"     = "Homogeneity × Routine Nonmanual × Redistribution",
              "homclass3_V_gc:dclass6resSelf-employed:abs_red"               = "Homogeneity × Self-employed × Redistribution",
              "homclass3_V_gc:dclass6resSkilled working class:abs_red"       = "Homogeneity × Skilled Working Class × Redistribution",
              "homclass3_V_gc:dclass6resUnskilled working class:abs_red"     = "Homogeneity × Unskilled Working Class × Redistribution",

              # 3-way interactions: × Welfare State
              "homclass3_V_gc:dclass6resLower Service class:wstate2"         = "Homogeneity × Lower Service × Welfare State",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:wstate2"     = "Homogeneity × Routine Nonmanual × Welfare State",
              "homclass3_V_gc:dclass6resSelf-employed:wstate2"               = "Homogeneity × Self-employed × Welfare State",
              "homclass3_V_gc:dclass6resSkilled working class:wstate2"       = "Homogeneity × Skilled Working Class × Welfare State",
              "homclass3_V_gc:dclass6resUnskilled working class:wstate2"     = "Homogeneity × Unskilled Working Class × Welfare State",
              # 3-way interactions: × GDP
              "homclass3_V_gc:dclass6resLower Service class:loggdppercapita"         = "Homogeneity × Lower Service × GDP",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:loggdppercapita"     = "Homogeneity × Routine Nonmanual × GDP",
              "homclass3_V_gc:dclass6resSelf-employed:loggdppercapita"               = "Homogeneity × Self-employed × GDP",
              "homclass3_V_gc:dclass6resSkilled working class:loggdppercapita"       = "Homogeneity × Skilled Working Class × GDP",
              "homclass3_V_gc:dclass6resUnskilled working class:loggdppercapita"     = "Homogeneity × Unskilled Working Class × GDP"              
              )

>>>>

```{r tableS2, results='asis'}
set1 <-  RColorBrewer::brewer.pal(n = 8, name = "Set1")
options(ggplot2.discrete.fill = set1)
options(ggplot2.discrete.colour = set1)
ggplot2::theme_set(ggplot2::theme_bw())
ggplot2::theme_update(text=ggplot2::element_text(size=15,  family="serif"))

@@

ccoef <- list(
              "dclass3res_VIntermediate class (III+IV)"="Intermediate Class",
              "dclass3res_VWorking Class (V+VI+VII)"="Working Class",
              homclass3_V_gc="Class-based network homogeneity (CWC)",
              "gini_disp" = "Income inequality (Gini index)",
              loggdppercapita = "GDP/capita",
              wstate2="Size of the welfare state",
              cpi = "Corruption Index",
              v2x_polyarchy = "Democracy (polyarchy index)",
              mig_share = "Migration (pop %)",
              union_den = "Union density",
              unemployment_rate = "Unemployment rate",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Intermediate Class × Homogeneity",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Working Class × Homogeneity",
              "homclass3_V_gc:gini_disp"= "Homogeneity x Income Inequality",
              "dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Income Inequality",
              "dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Income Inequality",
              "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Homogeneity × Income Inequality",
              "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Homogeneity × Income Inequality")

htmlreg(models_macro,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       file = here::here("output/tables/tableS02.html"),
       caption = paste("Table S2: Multilevel models for country-level factors,
                       income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars. The depedent variable and country-level variables are in standardized (z-score)",
       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
       custom.coef.map = ccoef,
      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
      # custom.gof.rows = list("Controls"=rep("Yes",4)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual")
      )
```

@@

# Double cross-level interaction Gini and Welfare State Size (Index)------------
int_xlvl_gini_wstate <- 
  lmer(egal~ 
         homclass3_V_gc+
         know_total_gc+
         dclass3res_V+
         female_gc+agenum_gc+
         homclass3_V_gc*dclass3res_V*gini_disp + 
         homclass3_V_gc*dclass3res_V*wstate2 + 
         (homclass3_V_gc+dclass3res_V|country2),data=dfreg,weights = WEIGHT)

@@

ccoef <- list(
  # Class
  "dclass3res_VIntermediate class (III+IV)" = "Intermediate Class",
  "dclass3res_VWorking Class (V+VI+VII)" = "Working Class",

  # Homogeneity
  homclass3_V_gc = "Class-Based Network Homogeneity (CWC)",

  # Class × Homogeneity
  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV)" = "Intermediate Class × Homogeneity",
  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII)" = "Working Class × Homogeneity",

  # Macro variables
  gini_disp = "Income Inequality (Gini Index)",
  ilo_taxrev = "Tax Revenue (% of GDP)",
  ilo_govspe = "Government Spending (% of GDP)",
  abs_red = "Redistribution",
  wstate2 = "Welfare State Size",
  loggdppercapita = "GDP per Capita (Log)",

  # Homogeneity × Macro
  "homclass3_V_gc:gini_disp" = "Homogeneity × Income Inequality",
  "dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Income Inequality",
  "dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Income Inequality",
  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):gini_disp" = "Intermediate Class × Homogeneity × Income Inequality",
  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):gini_disp" = "Working Class × Homogeneity × Income Inequality",

  "homclass3_V_gc:ilo_taxrev" = "Homogeneity × Tax Revenue",
  "dclass3res_VIntermediate class (III+IV):ilo_taxrev" = "Intermediate Class × Tax Revenue",
  "dclass3res_VWorking Class (V+VI+VII):ilo_taxrev" = "Working Class × Tax Revenue",  
  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_taxrev" = "Intermediate Class × Homogeneity × Tax Revenue",
  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_taxrev" = "Working Class × Homogeneity × Tax Revenue",

  "homclass3_V_gc:ilo_govspe" = "Homogeneity × Government Spending",
  "dclass3res_VIntermediate class (III+IV):ilo_govspe" = "Intermediate Class × Government Spending",
  "dclass3res_VWorking Class (V+VI+VII):ilo_govspe" = "Working Class × Government Spending",  
  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):ilo_govspe" = "Intermediate Class × Homogeneity × Government Spending",
  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):ilo_govspe" = "Working Class × Homogeneity × Government Spending",

  "homclass3_V_gc:abs_red" = "Homogeneity × Redistribution",
  "dclass3res_VIntermediate class (III+IV):abs_red" = "Intermediate Class × Redistribution",
  "dclass3res_VWorking Class (V+VI+VII):abs_red" = "Working Class × Redistribution",    
  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):abs_red" = "Intermediate Class × Homogeneity × Redistribution",
  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):abs_red" = "Working Class × Homogeneity × Redistribution",

  "homclass3_V_gc:wstate2" = "Homogeneity × Welfare State Size",
  "dclass3res_VIntermediate class (III+IV):wstate2" = "Intermediate Class × Welfare State Size",
  "dclass3res_VWorking Class (V+VI+VII):wstate2" = "Working Class × Welfare State Size",    
  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):wstate2" = "Intermediate Class × Homogeneity × Welfare State Size",
  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):wstate2" = "Working Class × Homogeneity × Welfare State Size",

  "homclass3_V_gc:loggdppercapita" = "Homogeneity × GDP per Capita",
  "dclass3res_VIntermediate class (III+IV):loggdppercapita" = "Intermediate Class × GDP per Capita",
  "dclass3res_VWorking Class (V+VI+VII):loggdppercapita" = "Working Class × GDP per Capita",      
  "homclass3_V_gc:dclass3res_VIntermediate class (III+IV):loggdppercapita" = "Intermediate Class × Homogeneity × GDP per Capita",
  "homclass3_V_gc:dclass3res_VWorking Class (V+VI+VII):loggdppercapita" = "Working Class × Homogeneity × GDP per Capita"
)

screenreg(models_interactions)
htmlreg(models_interactions,stars = c(0.001, 0.01, 0.05, 0.1),scalebox = 0.7,symbol = ".",
       file = here::here("output/tables/tableS03.html"),
       caption = paste("Table S3: Robustness analysis of the multilevel models for income inequality, network homogeneity and redistributive preferences"),
       custom.note = " Note: All individual level controls centered within cluster (group mean).  Standard errors in parentheses. %stars",
       caption.above = T,leading.zero = T,single.row = T,threeparttable = T,
       custom.coef.map = ccoef,
      # groups = list("Social Class (Ref.= Service Class)" = 2:3,"Homogeneity x Social Class"=7:8),
      # custom.gof.rows = list("Controls"=rep("Yes",4)),
      include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups",
                           "Var: Country (Intercept)",
                           "Var: Country Homogeneity",
                           "Var: Country Intermediate Class ",
                           "Var: Country Working Class",
                           "Cov: Country (Intercept), Homogeneity",
                           "Cov: Country (Intercept), Intermediate Class ",
                           "Cov: Country (Intercept), Working Class",
                           "Cov: Country Homogeneity, Intermediate Class",
                           "Cov: Country Homogeneity, Working Class",
                           "Cov: Country Intermediate Class, Working Class",
                           "Var: Residual")
      )
```

@@

## Model -  EGP3 - DIGCLASS - V to Working -----------------------------$ 
digclas1_VW_0<- lmer(egal~1 + dclass6res + female+agenum+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_1<- lmer(egal~1 + homclass3_V_res+know_total+(1|country2),data=dfreg,weights = WEIGHT)
digclas1_VW_3 <- update(digclas1_VW_1, . ~ . + dclass6res)
digclas1_VW_7 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res)
digclas1_VW_8 <- update(digclas1_VW_3, . ~ . +dclass6res*homclass3_V_res*gini_disp)
digclas1_VW <- list(digclas1_VW_0,digclas1_VW_1,
                    digclas1_VW_3,
                    # digclas1_VW_4,
                    #digclas1_VW_5,
                    # digclas1_VW_6,
                    digclas1_VW_7)

ccoef <- list("dclass6resLower Service class"="Lower Service",
              "dclass6resRoutine nonmanual class" = "Routine nonmanual",                 
              "dclass6resSelf-employed" = "Self-employed",                           
              "dclass6resSkilled working class" = "Skilled working",
              "dclass6resUnskilled working class" = "Unskilled working",
              homclass3_V_res="Class-based network homogeneity",
              know_total="Network size",              
              "homclass3_V_res:dclass6resLower Service class" = "Lower Service × Homogeneity",
              "homclass3_V_res:dclass6resRoutine nonmanual class" = "Routine nonmanual × Homogeneity",
              "homclass3_V_res:dclass6resSelf-employed"= "Self-employed × Homogeneity",
              "homclass3_V_res:dclass6resSkilled working class" = "Skilled working class × Homogeneity",
              "homclass3_V_res:dclass6resUnskilled working class" = "Unskilled working class × Homogeneity" 
              )

@@

htmlreg(digclas1_VW,stars = c(0.001, 0.01, 0.05, 0.1),single.row = T,symbol = ".",
       caption = paste("Table S4: Multilevel models for network homogeneity and redistributive preferences (6-class version)"),
       custom.note = "Note: Standard errors in parentheses. %stars",
       threeparttable = T,
       caption.above = T,leading.zero = T,
       custom.coef.map = ccoef,
       groups =
         list("Social Class (Ref.= Upper Service)" = 1:5,
              "Social Class × Homogeneity"=8:12),
      custom.gof.rows = list("Controls"=c("Yes",rep("Yes",3))),include.loglik = FALSE,include.aic = FALSE,
      custom.gof.names = c(NA,NA,"Num. groups","Var: Country (Intercept)","Var: Residual"),
      file = here::here("output/tables/tableS04.html")
      )
```

@@

ccoef <- list(homclass3_V_gc="Class-based network homogeneity",
              know_total="Network size",
              "dclass6resLower Service class"="Lower Service",
              "dclass6resRoutine nonmanual class" = "Routine nonmanual",                 
              "dclass6resSelf-employed" = "Self-employed",                           
              "dclass6resSkilled working class" = "Skilled working",
              "dclass6resUnskilled working class" = "Unskilled working",
              "homclass3_V_gc:dclass6resLower Service class" = "Homogeneity × Lower Service",
              "homclass3_V_gc:dclass6resRoutine nonmanual class" = "Homogeneity × Routine nonmanual",
              "homclass3_V_gc:dclass6resSelf-employed"= "Homogeneity × Self-employed",
              "homclass3_V_gc:dclass6resSkilled working class" = "Homogeneity × Skilled working class",
              "homclass3_V_gc:dclass6resUnskilled working class" = "Homogeneity × Unskilled working class",

@@

              # 3-way interactions: × Gini
              "homclass3_V_gc:gini_disp" = "Homogeneity × Gini",
              "dclass6resLower Service class:gini_disp"     = "Lower Service × Gini",
              "dclass6resRoutine nonmanual class:gini_disp" = "Routine Nonmanual × Gini",
              "dclass6resSelf-employed:gini_disp"           = "Self-employed × Gini",
              "dclass6resSkilled working class:gini_disp"   = "Skilled Working Class × Gini",
              "dclass6resUnskilled working class:gini_disp" = "Unskilled Working Class × Gini",
              "homclass3_V_gc:dclass6resLower Service class:gini_disp"         = "Homogeneity × Lower Service × Gini",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:gini_disp"     = "Homogeneity × Routine Nonmanual × Gini",
              "homclass3_V_gc:dclass6resSelf-employed:gini_disp"               = "Homogeneity × Self-employed × Gini",
              "homclass3_V_gc:dclass6resSkilled working class:gini_disp"       = "Homogeneity × Skilled Working Class × Gini",
              "homclass3_V_gc:dclass6resUnskilled working class:gini_disp"     = "Homogeneity × Unskilled Working Class × Gini",

              # 3-way interactions: × Tax Revenue
              "homclass3_V_gc:ilo_taxrev" = "Homogeneity × Tax Revenue",
              "dclass6resLower Service class:ilo_taxrev"     = "Lower Service × Tax Revenue",
              "dclass6resRoutine nonmanual class:ilo_taxrev" = "Routine Nonmanual × Tax Revenue",
              "dclass6resSelf-employed:ilo_taxrev"           = "Self-employed × Tax Revenue",
              "dclass6resSkilled working class:ilo_taxrev"   = "Skilled Working Class × Tax Revenue",
              "dclass6resUnskilled working class:ilo_taxrev" = "Unskilled Working Class × Tax Revenue",              
              "homclass3_V_gc:dclass6resLower Service class:ilo_taxrev"         = "Homogeneity × Lower Service × Tax Revenue",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:ilo_taxrev"     = "Homogeneity × Routine Nonmanual × Tax Revenue",
              "homclass3_V_gc:dclass6resSelf-employed:ilo_taxrev"               = "Homogeneity × Self-employed × Tax Revenue",
              "homclass3_V_gc:dclass6resSkilled working class:ilo_taxrev"       = "Homogeneity × Skilled Working Class × Tax Revenue",
              "homclass3_V_gc:dclass6resUnskilled working class:ilo_taxrev"     = "Homogeneity × Unskilled Working Class × Tax Revenue",

              # 3-way interactions: × Government Spending
              "homclass3_V_gc:ilo_govspe" = "Homogeneity × Gov. Spending",
              "dclass6resLower Service class:ilo_govspe"     = "Lower Service × Gov. Spending",
              "dclass6resRoutine nonmanual class:ilo_govspe" = "Routine Nonmanual × Gov. Spending",
              "dclass6resSelf-employed:ilo_govspe"           = "Self-employed × Gov. Spending",
              "dclass6resSkilled working class:ilo_govspe"   = "Skilled Working Class × Gov. Spending",
              "dclass6resUnskilled working class:ilo_govspe" = "Unskilled Working Class × Gov. Spending",                
              "homclass3_V_gc:dclass6resLower Service class:ilo_govspe"         = "Homogeneity × Lower Service × Gov. Spending",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:ilo_govspe"     = "Homogeneity × Routine Nonmanual × Gov. Spending",
              "homclass3_V_gc:dclass6resSelf-employed:ilo_govspe"               = "Homogeneity × Self-employed × Gov. Spending",
              "homclass3_V_gc:dclass6resSkilled working class:ilo_govspe"       = "Homogeneity × Skilled Working Class × Gov. Spending",
              "homclass3_V_gc:dclass6resUnskilled working class:ilo_govspe"     = "Homogeneity × Unskilled Working Class × Gov. Spending",

              # 3-way interactions: × Redistribution
              "homclass3_V_gc:abs_red" = "Homogeneity × Redistribution",
              "dclass6resLower Service class:abs_red"     = "Lower Service × Redistribution",
              "dclass6resRoutine nonmanual class:abs_red" = "Routine Nonmanual × Redistribution",
              "dclass6resSelf-employed:abs_red"           = "Self-employed × Redistribution",
              "dclass6resSkilled working class:abs_red"   = "Skilled Working Class × Redistribution",
              "dclass6resUnskilled working class:abs_red" = "Unskilled Working Class × Redistribution",                
              "homclass3_V_gc:dclass6resLower Service class:abs_red"         = "Homogeneity × Lower Service × Redistribution",
              "homclass3_V_gc:dclass6resRoutine nonmanual class:abs_red"     = "Homogeneity × Routine Nonmanual × Redistribution",
              "homclass3_V_gc:dclass6resSelf-employed:abs_red"               = "Homogeneity × Self-employed × Redistribution",
              "homclass3_V_gc:dclass6resSkilled working class:abs_red"       = "Homogeneity × Skilled Working Class × Redistribution",
              "homclass3_V_gc:dclass6resUnskilled working class:abs_red"     = "Homogeneity × Unskilled Working Class × Redistribution",
